### 2014-02-19 thesis/src/chapters/chapter-implementation.tex
Thesis: Cloud-SAP as self-adaptive system
Thesis: autoscaling subsystem goals

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-implementation/hlo-deployment}
  \end{center}
  \caption{Deployment diagram of a Cloud-SAP implementation}
  \label{fig:hlo-deployment}
\end{figure}

@@

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=\textwidth]{chapter-implementation/auto-scaling-subsystem-deployment}
  \end{center}
  \caption{Deployment diagram of a auto-scaling subsystem}
  \label{fig:auto-scaling-subsystem-deployment}
\end{figure}

>>>>

\newpage
\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-implementation/hlo-deployment}
  \end{center}
  \caption{System's deployment diagram}
  \label{fig:hlo-deployment}
\end{figure}

@@

\subsection{Objectives and structure}
The onus is on auto-scaling subsystem to:
\begin{itemize}
 \item scale applications in the most cost effective way
 \item handle application deployment requests and pass them to a cloud provider 
\end{itemize}

As overview states, this subsystem is in fact a loosely coupled group of three autonomic managers, cooperating together to achieve aforementioned subsystem's goals. System is structured (figure \ref{fig:auto-scaling-subsystem-deployment}) on top of that observation:

\begin{asparaenum}
 \item[\textbf{Container manager}]
 \item[\textbf{Stack manager}]
 \item[\textbf{Cloud instance manager}]
 \item[\textbf{Cloud provider client}]
 \item[\textbf{Cloud broker}]
 \item[\textbf{Cloud provider (OpenNebula and OpenVZ nodes)}]
\end{asparaenum}

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=\textwidth]{chapter-implementation/auto-scaling-subsystem-deployment}
  \end{center}
  \caption{Deployment diagram of auto-scaling subsystem}
  \label{fig:auto-scaling-subsystem-deployment}
\end{figure}

\subsection{Container manager}

\subsubsection{Objectives}
\subsubsection{Implementation details}
\subsubsection{Control loop iteration}

\subsection{Stack manager}

\subsubsection{Objectives}
\subsubsection{Implementation details}

\subsection{Cloud instance manager}

\subsubsection{Objectives}
\subsubsection{Implementation details}
